%
% $Id: ch04_implementation.tex
%
%   *******************************************************************
%   * SEE THE MAIN FILE "AllegThesis.tex" FOR MORE INFORMATION.       *
%   *******************************************************************
%
\chapter{Implementation}\label{ch:implem}

The table below describes the timeline that I have envisioned for my project.
This timeline is subject to change as some aspects of the timeline are dependent
on things running smoothly, which is bound to not always be the case. This is
subject to change also due to my schedule for the next two semesters.

\section{TimeLine}

\begin{table}[htbp]
 \centering
 \begin{tabular}{|l|l|}
 \hline
   {\textbf{Goal}}  &  {\textbf{Date}} \\ \hline
   Final Research on Search Engines &   Late November 2019    \\ \hline
   Start Early Process of Building a Search Engine & Early December 2019    \\ \hline
   Get Tooling PDF's Converted In The Search Engine &  Early January  \\ \hline
   Make Algorithm To Find Tools EDP &  Late January 2020    \\ \hline
   Finialize Search Engine &  Early Feburary 2020    \\ \hline
   Bug Fixing &  Late Feburary   \\ \hline
   Data Collection and Analyzing & Early March 2020 \\ \hline
 \end{tabular}
\caption{Timeline}
\label{latexprocess}
\end{table}


\section{Evaluate}


Due to the nature of building an search engine application and all of the complex algorithms that come with the app. This will lead to needing a large amount of time to complete my final research to make sure I understand everything completely. This will include deciding the structure of my search engine and how to implement it to read tooling catalogs. From here, the next step will be to begin implementing the different parts of the algorithms starting with finding tools using the edp number algorithm. After all the algorithms are completed they will be combined into one whole program and placed in the application. This will take some time as there are complex formulas that have to be figured out to get the application to be able to run. Then I would finalize the search engine and make any last improvements. I will than fix any bugs found in the applicaton to make sure the search engine works smoothly with no problems.  Lastly, I will just need a little bit of time to finish analyzing and gather results for my project.
