%
% $Id: conclusion.tex
%
%   *******************************************************************
%   * SEE THE MAIN FILE "AllegThesis.tex" FOR MORE INFORMATION.       *
%   *******************************************************************
%

\chapter{Discussion and Future Work}\label{ch:conclusion}

There are a variety of advantages that could arise from completing this project. One objective that could arise from this project is that I gain a full understanding of making a search engine application. That is helpful because it could speed up the process of implementing tools into another database for example WINTOOL. This would accompany the possibility that I can create a new method of building an application that is more secure and overall better than its current components. This is something that I feel will be very feasible for me to complete, I will have a lot of time to figure out the core components of the algorithm, mainly how to convert catalogs in the search engine.  This process will be very important for the rest of the project and will greatly affect the feasibility of making the application more user-friendly. The impact that it will have on the community of computer science is opening the influence of technology with the tooling industry. There haven't been any breakthroughs involving the way to find and organize tools with technology so that will open the minds of how people in the tooling industry think from this point forward. Some avenues of future work are connecting the search engine to the WINTOOL database. My goal is to eventually be able to use the search engine to search for an edp number and have the information automatically converted to the WINTOOL database. That would allow a user to skip the data entry step of individually searching for every tool and just allow the user to pick a catalog and type in a edp number and have all the information downloaded in the system. 
